\sys: Controllable Program Regeneration

### 2025-06-15 paper/draft.tex
Fix dup word
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\heading{Failure-driven refinement}
When a candidate fails verification, \sys treats this as a feedback signal. Instead of discarding the regeneration attempt wholesale, the system uses the failure to revise or re-execute the synthesis phase. This may take several forms:
\begin{itemize}
  \item \emph{Retrying synthesis}: A fresh LLM call with the same plan but a different generation path.
  \item \emph{Feedback loop}: \sys will provide the previous regeneration attempt 
    as an additional context to the LLM, together with with an explanation of the properties that were violated, prompting it to adapt its output based on prior failures.
    This mode is only activated if the verifier knows that the output will not to taint
    followupp regeneration attempts.
  \item \emph{Fallback handling}: If a function repeatedly fails validation, \sys may leave the original version intact or mark it for manual inspection.
\end{itemize}

>>>>

\heading{Failure-driven refinement}
When a candidate fails verification, \sys treats this as a feedback signal. Instead of discarding the regeneration attempt wholesale, the system uses the failure to revise or re-execute the synthesis phase. This may take several forms:
\begin{itemize}
  \item \emph{Retrying synthesis}: A fresh LLM call with the same plan but a different generation path.
  \item \emph{Feedback loop}: \sys will provide the previous regeneration attempt 
    as an additional context to the LLM, together with an explanation of the properties that were violated, prompting it to adapt its output based on prior failures.
    This mode is only activated if the verifier knows that the output will not to taint
    followupp regeneration attempts.
  \item \emph{Fallback handling}: If a function repeatedly fails validation, \sys may leave the original version intact or mark it for manual inspection.
\end{itemize}
